%%%%%%%%%%%%%%%%%%%% Intro to the application

\paragraph{Overview:}

Coordinated operation of multiple autonomous robots (multi-robot systems) has many important real-world applications \cite{multirobot2005,multirobotsurvey2013}.
For example, in a rescue, security, or disaster response mission, several autonomous aerial robots can coordinate to survey an area, monitor some target objects or activities, and guide ground robots or vehicles to complete complex tasks such as delivering aids.
In such applications, each robot is autonomous but has the capability to coordinate efficiently and safely with other robots to complete a shared mission, often in a distributed manner without any central coordinator.
Such distributed coordination is essential in real-world applications where the environment is constantly and unexpectly changing, but is also very challenging.
The Intelligent Control Systems (ICONS) Lab at NAU, directed by co-PI Nghiem, is developing distributed control and planning methods for multi-robot systems on a robotics platform that includes small quadcopters and four fully autonomous vehicles.
One of the most critical challenges of this research direction is the guarantee of the performance, in particular the safety, of a coordination plan, which is typically implemented in C code on the embedded computers of the robots and usually involves wireless inter-robot communication, sensing, and actuation.

\paragraph{Problem:}

Validation of a distributed coordination method for a multi-robot system is currently performed using a mix of theoretical proofs (for limited settings), extensive computer-based simulations, simulation-based falsification techniques, and real experiments.
Even when a method is validated by mathematical proofs and/or simulations, it often fails in real experiments due to discrepancies between models and real systems and between the method's design and its software implementation on the robots.
The methods and tools proposed in this project will help control and robotics researchers, who usually do not have expertise in software verification and testing, overcome this challenge.


\paragraph{Plan:}

First, we will model a coordination plan / algorithm for multiple robots as a potentially very complex network of timed automata.
Performance specifications will be expressed in temporal logics, e.g., the Signal Temporal Logic (STL) \cite{donze2010robust}, and checked against the model using verification and testing tools such as \uppaal or S-TaLiRo \cite{annpureddy2011s}.
This step ensures that the original coordination algorithm has no subtle flaws that lead to violations of the performance specifications.
An implementation of the algorithm in C code, distributed among the robots, will be developed by a robotics/control student.
The implementation will then be automatically annotated with the desired performance specifications by the tools developed in this project.
Next, we will attempt to prove, using our tools, that components of the code faithfully represent the coordination algorithm.
Given the complexity of multi-robot coordination algorithms, we do not expect \framac to be able to prove all the components of the implementation correct.
Consequently, we will use DeepState, driven by harnesses automatically generated by our tools, to generate tests of the implementation components not yet verified by \framac.
Finally, we will perform experiments of the coordination algorithm with aerial and ground robots in the ICONS Lab.
This case study will be conducted by a robotics/control graduate student in the ICONS Lab, using the software tools developed in this project.
Given the different nature and complexity of this application compared to the first case study on SEGA, the obtained feedback will be much valuable for the development and improvement of the proposed methods and tools for practical usages in a wide spectrum of real systems.


%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
