\section{Research Plan}

%\subsection{From Timed Automata to \framac}
%\label{sec:ta2framac}
%\input{automatatoframac}

\subsection{DeepState and Automated Test Generation}
\label{sec:framac2deepstate}
\input{framactodeepstate}

\subsection{Other DeepState Extensions}

\paragraph{Bounded Model Checking:}
\input{cbmcplan}

\paragraph{Explicit-State Model Checking:}
\input{spinplan}

\paragraph{Timed Automata Model Skeleton Generation:}
As noted above, one of our core assumptions is that timed automata can
model the underlying protocols in many embedded systems.  However,
writing timed automata models using \uppaal~\cite{uppaal} and
\prism~\cite{KNP2011:CAV} is at present a skill only a small number of
embedded engineers have mastered.  In order to encourage more
engineers to make use of these powerful formalisms, we propose 1) to
enable DeepState to generate \emph{traces} of the annotations related
to timing that are covered during a run and 2) to build a tool to
combine and reconcile these traces into a skeleton model for \uppaal~\cite{uppaal} or
\prism~\cite{KNP2011:CAV} (as has been done to some extent for Java~\cite{liva2017extracting}).  The structure of code (function locations
of DeepState annotations) will be used to form the structure of the
model.  Additional annotations for, e.g. probabilities, may need to be
added if not present in the code annotations, though DeepState already
has a primitive support for expressing probabilities that we plan to extend.

\paragraph{Other Tools:}  Galois Inc. has expressed strong interest in
an (unpaid) ongoing research collaboration to integrate their C and
C++ relevant tools into DeepState as well, to support our general vision.

\subsection{Case Studies} % for Ecological Monitoring and Control}
\label{sec:case-study}

The above briefly introduces a number of problems that we know in advance must
be dealt with in order to enable a pathway for combining formal,
static, and dynamic analysis.    At heart, however, we aim to allow
\emph{case studies} to prioritize our efforts, and
are certain that other challenges will arise during these efforts.
The studies informing this research is the embedded software of wireless sensor nodes used in the Southwest Experimental Garden Array (SEGA)~\cite{ClaEtAl11,GhoEtAl2014,BelEtAl2015} and of wireless sensor nodes and mobile robots in the Distributed Sensing \& Computing Over Sparse Environments (DISCOVER) Platform.

\input{casestudysega}

% \subsubsection{Case Study: Distributed Coordination in Multi-Robot Systems}
% \label{sec:case-study-robots}

% \input{casestudyrobots}

\subsection{Work Plan}
\input{workplan}

\section{Contributions to Formal Methods and the Field}
\label{sec:contributions}
\input{contributions}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
