\begin{wrapfigure}{r}{.35\textwidth}
%\begin{figure}[!tp]
%  \centering
  \resizebox{.35\textwidth}{!}{%
  \begin{ganttchart}[%Specs
    hgrid style/.style={black, dotted},
    vgrid, %={*2{black,dotted}, *1{black, dashed},
      %*2{black,dotted}, *1{black, dashed},
      %*2{black,dotted}, *1{black, dashed},
      %*2{black,dotted}, *1{black, solid}},
    x unit=3mm,
    y unit chart=5mm,
    y unit title=5mm,
    %time slot format=isodate,
    title height=1,
    milestone label font=\footnotesize,
    group label font=\bfseries\footnotesize,
    title label font=\bfseries\footnotesize,
    link/.style={->, thick},
    %bar/.style={fill=blue},
    %bar height=0.7,
    %group right shift=0,
    %group top shift=0.7,
    %group height=.3,
    %group peaks width={0.2},
    %inline
    ]{1}{36}
    % labels
    % \gantttitle{A two-years project}{24}\\  % title 1 
    \gantttitle[]{Year 1}{12}                 % title 1
    \gantttitle[]{Year 2}{12}
    \gantttitle[]{Year 3}{12} \\
    \gantttitle{Q1}{3}                      % title 3
    \gantttitle{Q2}{3}
    \gantttitle{Q3}{3}
    \gantttitle{Q4}{3}
    \gantttitle{Q1}{3}
    \gantttitle{Q2}{3}
    \gantttitle{Q3}{3}
    \gantttitle{Q4}{3}
    \gantttitle{Q1}{3}
    \gantttitle{Q2}{3}
    \gantttitle{Q3}{3} 
    \gantttitle{Q4}{3}\\    

    % \ganttgroup[inline=false]{Group 1}{1}{5}\\ 
    % \ganttbar[progress=10,inline=false]{Planning}{1}{4}\\
    % \ganttmilestone[inline=false]{Milestone 1}{9} \\

    % \ganttgroup[inline=false]{Group 2}{6}{12} \\ 
    % \ganttbar[progress=2,inline=false]{test1}{10}{19} \\
    % \ganttmilestone[inline=false]{Milestone 2}{17} \\
    % \ganttbar[progress=5,inline=false]{test2}{11}{20} \\
    % \ganttmilestone[inline=false]{Milestone 3}{22} \\       

    % \ganttgroup[inline=false]{Group 3}{13}{24} \\ 
    % \ganttbar[progress=90,inline=false]{Task A}{13}{15} \\ 
    % \ganttbar[progress=50,inline=false, bar progress label node/.append style={below left= 10pt and 7pt}]{Task B}{13}{24} \\ \\
    % \ganttbar[progress=30,inline=false]{Task C}{15}{16}\\ 
    % \ganttbar[progress=70,inline=false]{Task D}{18}{20} \\ 

    \ganttgroup[
        group/.append style={fill=blue}
    ]{WP1}{1}{36}\\ [grid]
    \ganttbluebar[
        name=T11
    ]{T1.1}{1}{6}\\ [grid]
    \ganttbluebar[
        name=T12
    ]{T1.2}{7}{24}\\ [grid]
    \ganttbluebar[
        name=T13
    ]{T1.3}{25}{36}\\ [grid]
    % \ganttlinkedbluebar{}{2014-10-7}{2014-10-10}
    % \ganttlinkedbluebar{}{2014-10-14}{2014-10-15}
    % \ganttlinkedbluebar{}{2014-10-17}{2014-10-17}
    % \ganttlinkedbluebar[name=FMEend]{}{2014-10-21}{2014-10-24}
    % \ganttlinkedbluebar{}{2014-10-28}{2014-10-31}\\ [grid]
    % \ganttbluebar[name=Manual]{Manual}{2014-10-30}{2014-10-31}
    % \ganttlinkedbluebar{}{2014-11-4}{2014-11-7} \ganttnewline[thick, black]

    \ganttgroup[
        group/.append style={fill=blue}
    ]{WP2}{1}{36}\\ [grid]
    \ganttbluebar[
        name=T21
    ]{T2.1}{1}{6}\\ [grid]
    \ganttbluebar[
        name=T22
    ]{T2.2}{7}{24}\\ [grid]
    \ganttbluebar[
        name=T23
    ]{T2.3}{25}{36}\\ [grid]

    \ganttgroup[
        group/.append style={fill=blue}
    ]{WP3}{1}{6}
    \ganttgroup[
        group/.append style={fill=blue}
    ]{}{19}{36}\\ [grid]
    \ganttbluebar[
        name=T311
    ]{T3.1}{1}{6}\\ [grid]
    \ganttbluebar[
        name=T312
    ]{T3.2}{19}{36}\\ [grid]
    \ganttbluebar[
        name=T321
    ]{T4.1}{25}{27}\\ [grid]        
    \ganttbluebar[
        name=T322
    ]{T4.2}{28}{36}
    % %Implementing links
    % \ganttlink[link mid=0.75]{Documentation}{FME}
    % \ganttlink{FMETutorial}{FME}
  \end{ganttchart}}%
\caption{Project schedule.}%
\label{fig:project-schedule}%
% \end{figure}
%\vspace{-0.4in}
\end{wrapfigure}

The project will be organized into two phases, described by work
packages.  In the first phase, T3.1 will be conducted along with T1.1 and will inform the development in these tasks.
In the second phase, the focus will be on the application of tools in
T1.2 in tandem with T2.
Tasks related to case studies (tasks T4.1, and T4.2), whose results
and feedback will help refine the developed tools will be especially
emphasized in the final phases of the project.
The timeline of the tasks will be structured as shown in Figure~\ref{fig:project-schedule}.

\paragraph{Work Package 1 (WP1):}  This work package concerns the
development of and use of \acsl and\eacsl extensions for use in
embedded system implementation
code.


$\bullet$ T1.1: This task will consider needed extensions for handling
real-world embedded systems.  In particular, there will be a focus on
a study of the formal semantics of timed
automaton networks defined in \uppaal and \prism, to determine the
extnet to which shared semantics can be assigned making it possible to
carry implementation annotations into such formal models (see T4.2)
and, in theory, translate properties from such models into implementation annotations.  As such, there will be close collaboration and iterative design steps between this task and the other work packages. %WP3 (Application).

$\bullet$ T1.2: This task will take feedback from applications of
tools to generate tests and proofs (T2) into account, to add annotations
that are fundamentally more concerned with heuristic guidance for
tools than for correctness per-se.

One Ph.D. student will be needed to conduct the work in this work package, which will last for the entire duration of the project.
The student will collaborate closely with students in WP2 and WP3.

\paragraph{Evaluation:} Evaluation of
WP1 will be determined by ability of embedded engineers to agree that
the key properties, including those related to timed automata models, to be checked are (1) all representable by the
annotations (2) easy to construct (given the basic difficulty of
systems specification) (3) easy to read when produced by others and
(4) maintainable after introduction.

\paragraph{Work Package 2 (WP2):}  This work package covers
methods and tools to automatically translate \acsl/\eacsl-annotated code in
into a \deepstate test harness (Section~\ref{sec:framac2deepstate}),
the development of DeepState back-ends for CBMC and SPIN, with
appropriate mechanisms to ease the use of these tools, and
improvements to fuzzers to improve test generation:
\begin{itemize}[labelsep=3pt,leftmargin=12pt]
\item T2.1: This task will optimize the implementation of symbolic
  execution and fuzzing in DeepState, so that \acsl/\eacsl annotations
  and extensions from WP1 can be used in DeepState to test implementation code.
\item T2.2: This task will develop DeepState back-ends for CBMC and
  SPIN, as well as inform annotations needed to handle loop bounds,
  memory tracking and matching, as well as feedback from fuzzing.
\item T2.3: In this task, we will augment \deepstate and fuzzers in
  the multiple ways described in Section~\ref{sec:framac2deepstate},
  in order to make them more useful in our context.  
\end{itemize}

The execution of this work package will span the entire duration of the project.
One Ph.D. student will work on the tasks in WP2, and collaborate with
the students in WP1 and WP3.

\paragraph{Evaluation:} Evaluation of
Work Package 2 will be determined by the successful generation of
DeepState harnesses for \acsl/\eacsl annotated code, and the successful
application of those harnesses to generate tests for realistic
systems.  We will again use benchmarks and simple examples to some
extent, but primarily rely on our connection to case studies.
In the case of test generation, in addition to faults
detected, we will use code coverage and other standard
benchmarks~\cite{FuzzerHicks}.  We expect to publish papers on
advances in fuzzing technology, in particular, as well as papers on
fundamental issues arising from the CBMC and SPIN back-ends with
respect to handling loop bounds and memory tracking/matching.

\paragraph{Work Package 3 (WP3):}  This work package will focus on the applications described in Sections~\ref{sec:case-study} and \ref{sec:case-study-robots}, as both a way to inform the methodology and tool developments in the other work packages and case studies in two completely different domains to validate our methods and tools.
WP3 includes two case studies:
\paragraph{SEGA case study (Section~\ref{sec:case-study}):} This application is divided into two tasks:
\noindent  \begin{itemize}[labelsep=3pt,leftmargin=12pt]
  \item T3.1: In this task, the existing SEGA system will be
    studied thoroughly to extract the key requirements and
    characteristics of the embedded system implementation.  Timed
    automaton models of the communication protocol used in the system,
    at different levels of abstraction, may be developed and formally
    verified in \uppaal and/or \prism, to inform task T1.1. The system information and models
    resulting from this task will inform the semantics design and method
    developments in WP1 and WP2. As time allows, and pending results
    with respect to the communication protocol, we will extend this to include sensing
    and control elements.
  \item T3.2: This task will apply the tools developed in WP1 and WP2
    to the SEGA system, in order to detect and fix the particular bugs in the current
    implementation that cause the intermittent failures mentioned in
    Section~\ref{sec:case-study}.  It will also provide feedback to
    the other work packages to refine and improve our tools.
  \end{itemize}

\paragraph {Robotics case study (Section~\ref{sec:case-study-robots}):} this study, in the last year of the project, is divided into two tasks:
\noindent \begin{itemize}[labelsep=3pt,leftmargin=12pt]
  \item T4.1: In this task, a multi-robot coordination algorithm
    currently used with our existing multi-robot system will be
    modeled as a network of timed automata.  Using our insights into
    the robotics application, we will express its performance
    specifications, particularly its safety requirements, in temporal
    logics and formally verify or test them in tools like \uppaal,
    \prism, or S-TaLiRo.  This task will extend the semantics and
    methods developed to applications beyond communication protocols,
    to identify further needed runtime extensions and semantic
    connections between timed automata theory, implementation
    annotations, and runtime checks.
  \item T4.2: This task will apply the tools developed in WP1 and WP2
    to the coordinated multi-robot system, in order to validate the
    implementation code and detect and fix its bugs.  It will also
    provide feedback to the other work packages to refine and improve
    the tools developed in this project.
    \item T4.3: This task will aim to use the work on the robotics
      effort to prototype a mapping from implementation code
      annotations in \acsl/\eacsl and extensions into skeletons of
      models in timed automata formalisms.  
  \end{itemize}

As the tasks in this work package are conducted in tandem with WP1 and WP2, to form a feedback loop with the developments in other work packages, it will last for the entire duration of the project.
We expect that groups of undergraduate students and two
Ph.D. students, who will join the project in the second and third
years, in collaboration with the Ph.D. students in WP1 and WP2, will
perform the work.

\paragraph{Evaluation:} In essence, this task \emph{is} the evaluation
aspect of our project, which forms one of the major thrusts of
the project.  The successful application of WP1 and WP2 tools to the case studies is
essentially the driving factor in determining our success in the
project.
%, and the key feedback to drive changes to our research
%priorities or technical choices.
The measure of success is (1) faults detected and corrected (2) functionality
proven correct using CBMC, symbolic execution engines, or SPIN (3) coverage and other measures
of generated tests and (4) reported usability and value by embedded
systems engineers, particularly students.  For T4.3, the evaluation
will be based on a formal comparison of the extracted skeleton with
full timed automata models developed by embedded systems experts. The
degree of 
success will be estimated based on the correspondence with a real model, and the completeness of
the skeleton, plus an informal judgment of the difficulty of taking
the skeleton and producing a usable full model.

%\subsubsection{Timeline}
%\label{sec:time-line}

